---
title: "Loaded Questions Scoring"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

suppressWarnings(library(knitr))

opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 3,
               message = FALSE, warning = FALSE, dpi = 96)

knit_print.data.frame = function(x, ...) {
      res = paste(c("", "", kable(x, row.names = FALSE)), collapse = "\n")
      asis_output(res)
}


```

```{r}
# Loaded Questions scoring

# This script reads a google drive worksheet with people's answers to the game
# "Loaded Questions" and scores those answers. Answers must be in a standard
# format! Anything in the Google sheet that is in rows of higher number than the
# number of players + 1 will be ignored, and anything in the columns of higher
# number than the number of questions + 1 will be ignored.

# !!! Important! You can't just source this document b/c it needs to interact
# with the Google API and get authorization! Run the "Authorization" section,
# give authorization, and then run the rest.

# Authorization -------------------------------------------------------------

library(googlesheets4)
library(googledrive)

MyURL <- "https://docs.google.com/spreadsheets/d/1Sc8_ulUgQjr5HbbDvvnQZzIcg0CkO7rCtNUczYfQvfM/edit#gid=2060014082"

```
```{r}
# Housekeeping -----------------------------------------------------------
library(gridExtra)
library(tidyverse)
library(ggpubr)
library(scales)
library(LaurasHelpers)

ThemeLaura <- function (base_size = 12, base_family = "") {
      theme_gray(base_size = base_size, base_family = base_family) %+replace%
            theme(
                  panel.background = element_rect(fill="white", color=NA),
                  panel.grid.minor.y = element_line(color = NA),
                  panel.grid.minor.x = element_line(color = NA),
                  panel.grid.major = element_line(colour = NA),
                  plot.background = element_rect(fill="white", colour=NA),
                  panel.border = element_rect(color="black", fill=NA),
                  strip.background = element_rect(color=NA, fill="white"),
                  legend.background = element_rect(color=NA, fill=NA),
                  legend.key = element_rect(color=NA, fill=NA)
            )
}

scale_colour_discrete <- function(...) scale_colour_brewer(..., palette="Set1")
scale_fill_discrete <- function(...) scale_fill_brewer(... , palette="Set1")

# Call up that theme before plotting graphs.
theme_set(ThemeLaura())

colRainbow <- colorRampPalette(c("gray20", "antiquewhite4", "firebrick3",
                                 "darkorange", "green3", "seagreen3",
                                 "cadetblue", "dodgerblue3", "royalblue4",
                                 "darkorchid4"))

blueGreen <- colorRampPalette(c("green3", "seagreen3", "cadetblue", "dodgerblue3",
                                "royalblue4"))


# Reading in the files -----------------------------------------------------

Questions <- sheets_read(MyURL, sheet = "Form Responses 1")

AllQ <- gsub("\n", " ", names(Questions))
names(AllQ) <- c("TimeStamp", "Player", paste0("Q", 1:(ncol(Questions)-4)),
                 "Email", "UntitledQ")
names(Questions) <- names(AllQ)

# Removing unnecessary columns. 
Questions <- Questions %>% select(-Email, -UntitledQ, -TimeStamp)

# Keeping only the actual questions in AllQ
AllQ <- AllQ[!(AllQ %in% c("Timestamp", "Name", "Email Address", "Untitled Question"))]

Players <- Questions %>% pull(Player) %>% str_to_title()

GuessSheets <- sheets_get(MyURL)$sheets %>% 
      filter(str_detect(name, "[Gg]uess")) %>% 
      pull(name)

# Including only people who answered this round.
GuessSheets <- GuessSheets[str_detect(GuessSheets, str_c(Players, collapse = "|"))]

# Manually removing old ones for now. 
GuessSheets <- GuessSheets[!str_detect(GuessSheets, "'s")]

Guesses.xl <- list()
for(i in GuessSheets){
      Guesses.xl[[i]] <- sheets_read(MyURL, sheet = i,
                                  range = cell_limits(ul = c(1, 1),
                                                      lr = c(length(Players) + 1,
                                                             2*length(AllQ))))
      # Guesses[[i]] <- sheets_read(MyURL, sheet = i)
      names(Guesses.xl[[i]]) <- 
            paste(c("Player", "Answer"), rep(names(AllQ), each = 2), sep = "_")
      Guesses.xl[[i]] <- Guesses.xl[[i]] %>% 
            mutate(SheetName = i)
}

# ch <- Guesses[[i]]
GA <- bind_rows(Guesses.xl)
GA$ID <- 1:nrow(GA)
GA <- GA %>% 
      gather(key = GA, value = Value, -SheetName, -ID) %>% 
      separate(GA, c("GA", "Question"), "_") %>% 
      filter(complete.cases(Value))

Guesses2 <- GA %>% filter(GA == "Player") %>% select(-GA) %>% rename("Player" = "Value")
Answers2 <- GA %>% filter(GA == "Answer") %>% select(-GA) %>% rename("Answer" = "Value")
Guesses <- full_join(Guesses2, Answers2) %>% 
      mutate(Guesser = sub(" guesses", "", SheetName)) %>% 
      select(-SheetName, -ID)

# Scoring -----------------------------------------------------------------

Questions <- Questions %>% 
      gather(key = "Question", value = "Answer", -Player) %>% 
      rename("CorrectAnswer" = "Answer")

Scores <- Guesses %>% left_join(Questions) %>% 
      mutate(Correct = Answer == CorrectAnswer) %>% 
      filter(Player != Guesser)

```
```{r}
# Setting up graphs

graphMostCorrect <- function(DF){
      
      NumColor <- DF %>% pull(Guesser) %>% unique() %>% length()
      
      ggplot(DF, aes(x = reorder(Guesser, desc(NumCorrect)), y = NumCorrect,
                     fill = Guesser)) + 
            geom_bar(stat = "identity") +
            scale_fill_manual(values = colRainbow(NumColor)) +
            xlab("Guesser") + ylab("Number of correct guesses") +
            theme(legend.position = "none")
      
}

```

# Q1: `r AllQ["Q1"]`

Actual answers:  

```{r}
Q1 <- Scores %>% filter(Question == "Q1", Correct == TRUE)

Questions %>% filter(Question == "Q1") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()

```

Who had the most correct answers? 

```{r}
MostCorrect_Q1 <- Q1 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q1)

```

For each player, who guessed their answer correctly?

```{r}

Q1 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q2: `r AllQ["Q2"]`

```{r}
Q2 <- Scores %>% filter(Question == "Q2", Correct == TRUE)

Questions %>% filter(Question == "Q2") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()

```

Who had the most correct answers? 

```{r}
MostCorrect_Q2 <- Q2 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q2)

```

For each player, who guessed their answer correctly?

```{r}

Q2 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q3: `r AllQ["Q3"]`

```{r}
Q3 <- Scores %>% filter(Question == "Q3", Correct == TRUE)

Questions %>% filter(Question == "Q3") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()

```

Who had the most correct answers? 

```{r}
MostCorrect_Q3 <- Q3 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q3)

```

For each player, who guessed their answer correctly?

```{r}

Q3 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q4: `r AllQ["Q4"]`

```{r}
Q4 <- Scores %>% filter(Question == "Q4", Correct == TRUE)

Questions %>% filter(Question == "Q4") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()

```

Who had the most correct answers? 

```{r}
MostCorrect_Q4 <- Q4 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q4)

```

For each player, who guessed their answer correctly?

```{r}

Q4 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q5: `r AllQ["Q5"]`

```{r}
Q5 <- Scores %>% filter(Question == "Q5", Correct == TRUE)

Questions %>% filter(Question == "Q5") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()


```

Who had the most correct answers? 

```{r}
MostCorrect_Q5 <- Q5 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q5)

```

For each player, who guessed their answer correctly?

```{r}

Q5 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q6: `r AllQ["Q6"]`

```{r}
Q6 <- Scores %>% filter(Question == "Q6", Correct == TRUE)

Questions %>% filter(Question == "Q6") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()


```

Who had the most correct answers? 

```{r}
MostCorrect_Q6 <- Q6 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q6)

```

For each player, who guessed their answer correctly?

```{r}

Q6 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q7: `r AllQ["Q7"]`

```{r}
Q7 <- Scores %>% filter(Question == "Q7", Correct == TRUE)

Questions %>% filter(Question == "Q7") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()


```

Who had the most correct answers? 

```{r}
MostCorrect_Q7 <- Q7 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q7)

```

For each player, who guessed their answer correctly?

```{r}

Q7 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Q8: `r AllQ["Q8"]`

```{r}
Q8 <- Scores %>% filter(Question == "Q8", Correct == TRUE)

Questions %>% filter(Question == "Q8") %>% select(Player, CorrectAnswer) %>% 
      rename("Actual answer" = "CorrectAnswer") %>% 
      kable()


```

Who had the most correct answers? 

```{r}
MostCorrect_Q8 <- Q8 %>% group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% arrange(desc(NumCorrect))

graphMostCorrect(MostCorrect_Q8)

```

For each player, who guessed their answer correctly?

```{r}

Q8 %>% group_by(Player) %>% 
      summarize(Who = str_c(Guesser, collapse = ", ")) %>% 
      rename("Who guessed correctly?" = "Who") %>% 
      kable()

```

# Overall scores  

Number of correct answers:  

```{r}

Final <- Scores %>% filter(Correct == TRUE) %>% 
      group_by(Guesser) %>% 
      summarize(NumCorrect = n()) %>% 
      ungroup() %>% 
      mutate(Guesser2 = paste(Guesser, NumCorrect, sep = "\n"))

ggplot(Final, aes(x = reorder(Guesser2, desc(NumCorrect)), y = NumCorrect,
                           fill = Guesser)) + 
      geom_bar(stat = "identity") +
      xlab("Guesser") + ylab("Number of correct guesses") +
      scale_fill_manual(values = colRainbow(length(Final$Guesser))) +
      theme(legend.position = "none")

```

Who knows you best? Who guessed your answers correctly the most? 

```{r}

Scores %>%
      filter(Correct == TRUE) %>% 
      group_by(Player, Guesser) %>% 
      summarize(NumCorrect = n()) %>% 
      group_by(NumCorrect, Player) %>% 
      summarize(Guesser = str_c(Guesser, collapse = " & ")) %>% 
      group_by(Player) %>% 
      summarize(KnownBestBy = Guesser[which.max(NumCorrect)],
                NumMatches = max(NumCorrect)) %>% 
      rename("Known best by" = "KnownBestBy", 
             "Number of correct guesses" = "NumMatches") %>% 
      kable()


```




